Reply To Examiners

### 2014-03-31 answer_thesis_examiner/answer_document.tex
auto

\usepackage{titlesec}
\newcommand{\sectionbreak}{\clearpage}

@@

>>>>

\usepackage{titlesec}
\newcommand{\sectionbreak}{\clearpage} %to give each section a new page

\usepackage{amsmath} %to have equation with no number

@@

Examiner No.3 expresses his doubt on two points.
First, that ``the determinant $|\Sigma|$ will be very small, leading to a very narrow PDF in Equation 4.1''.
And second that $\Sigma^{-1}$ is ill-defined.
I wish to highlight that Equation 4.1 is the PDF for the circular complex Gaussian distribution, which is widely used in POLSAR.
Its form, as repeated from equation 4.1, is written as:

\begin{align*}
  pdf(s;\Sigma)=\frac{1}{\pi^d |\Sigma|} e^{-s^{*T}\Sigma^{-1}s}
\end{align*}

This equation is also ill-defined where $|\Sigma|=0$, which is also the only time that $\Sigma^{-1}$ is ``ill-defined''.
In other words, the models proposed has the same assumption and validity with the widely-accepted circular complex Gaussian distribution model.
In POLSAR, $|\Sigma|=0$ most commonly happens when the dataset is in Single-Look format.
This restriction is clearly stated in the sentence that follows Equation 4.1: ``the covariance matrix is only defined on multiple data-points''.

It is partially for the second concern that log-transformation is proposed.
Since the original domain is multiplicative, the range of small values is, as also observed by Examiner No. 3, commonly found but extremely limited ($|\Sigma|$ ranges from $0+$ to $1$).
Log transformed domain not only changes the nature from multiplicative to additive, but also give this ``small'' range $(0,1)$ a much widely space $(-\infty,0)$.
In other words, it helps to expand the ``narrow'' distribution depicted in Equation 4.1 (when $|\Sigma|$ is small) to become another distribution whose shape does not dependent on $|\Sigma|$.

\begin{align*}
  pdf( \ln | \langle ss^{*T} \rangle|, \Sigma) = \ln |\Sigma| - \ln(2L)d + \sum^{d-1}_{i=0} \Lambda (2L-2i)
\end{align*}
